---
title: "Figure 4 supplementary material"
output:
  pdf_document: default
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---
```{r, echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(fig.width = 15, fig.height = 17, echo = FALSE, results = "hide", warning = FALSE, message = FALSE)
```

# Imports

```{r}
library(Metrics)
library(tidyverse)
library(reshape2)
library(scales)
library(ggpubr)
library(EpiDISH)
library(stringr)
library(grid)
library(ggpubr)

```

# Function definition

```{r}
# Does the typical deconvolution scatterplot comparing true proportions to certain deconvolution estimates. Called inside scatterplot_wrapper
scatterplot_truevsestimate <- function(merged_data, x, y, title, color){
    merged_data %>% dplyr::select(all_of(x),all_of(y)) %>%
    na.omit() -> to_plot
  
    to_plot.cor <- rcorr(data.matrix(to_plot[c(x,y)]), type = "pearson")
  
  if (to_plot.cor$P[x,y] == 0){
    p.val = "< 2.2e-16"
    } else {
      p.val = paste("=", signif(to_plot.cor$P[x,y],2))
    }
    to_plot.rmse = sqrt(colMeans((to_plot[,y] - to_plot[,x])^2, na.rm = T))
    
  
  stats <- paste("Pearson: R = ", round(to_plot.cor$r[x,y], 2),
               ", pval ", p.val, "\n",
               "RMSE = ", round(to_plot.rmse, 2), sep = "")
  
  ## plot
  your_plot <- ggplot(to_plot) +
    aes_string(x = x, y = y) +
    geom_point(color = color) +
    labs(title = title, subtitle = stats, x = "", y = "") +
    geom_smooth(method=lm) +
    theme_classic() +
    theme(
      plot.title=element_text(family='', face='bold', colour='black', size=25, margin=margin(t=50,b=-40)),
      plot.subtitle=element_text(family='', face='italic', colour='black', size=18, margin=margin(t=50,b=-40)),
      text = element_text(size=15)
  )
  
  return(your_plot)
}

# goes through the different celltypes estimates dataframe, filtering for those of a given decon_method  to compare them to the real celltype proportions of true_df, producing for each a scatterplot with scatterplot_truevsestimate.
scatterplot_wrapper <- function(true_df,
                                RNA_estimates,
                                methy_estimates,
                                RNA_meth,
                                name){

  sapply(list(RNA_estimates$Samples, methy_estimates$rowname), FUN = identical, true_df$Sample_ID) %>% stopifnot()
  
  # dataset prep
  RNA_estimates %>% 
    dplyr::select(starts_with(RNA_meth)) %>%
    rename_with(~str_remove(., RNA_meth)) %>%
    rename_with(~paste(.,"RNA", sep="_")) -> RNA_estimates_s
  
  methy_estimates %>% dplyr::select(-c(rowname))  %>%
    rename_with(~paste(.,"methy", sep="_")) -> methy_estimates_s
  
  RNA_estimates_s %>% bind_cols(methy_estimates_s, true_df) %>%
    mutate(Lymphocytes_RNA = B_RNA + CD4_RNA + CD8_RNA + NK_RNA,
           Macrophages_RNA = M0_RNA + M1_RNA + M2_RNA + Mono_RNA,
           Lymphocytes_methy =  B_methy + CD4_methy + CD8_methy + NK_methy + Treg_methy,
           Macrophages_methy = M0_methy + M1_methy + M2_methy + Mono_methy,
           Lymphocytes_avg = rowMeans(bind_cols(Lymphocytes_RNA, Lymphocytes_methy)),
           Macrophages_avg = rowMeans(bind_cols(Macrophages_RNA, Macrophages_methy)),
           Neu_avg = rowMeans(bind_cols(Neu_RNA, Neu_methy))) -> merged_data
  
  # plots
  celltype_trios <- tibble(Lymphocytes = c("Lymphocytes_RNA", "Lymphocytes_methy", "Lymphocytes_avg"),
                           Macrophages = c("Macrophages_RNA", "Macrophages_methy", "Macrophages_avg"),
                           Neutrophils = c("Neu_RNA", "Neu_methy", "Neu_avg"))
  
  colors <- list(Lymphocytes = "black",
                 Macrophages = "black",
                 Neutrophils = "black")
  
  RNA_title <- str_split(RNA_meth, '_', simplify = TRUE)[,2]
  
  titles <- list(RNA = RNA_title,
                 methy = "BPmetCan",
                 avg = "Average")
  
  resplots <- list()
  
  for (ct in names(celltype_trios)){ # ct correspond to the true_df celltype name
    
  
    RNA <- scatterplot_truevsestimate(merged_data, x = ct,
                                      y = celltype_trios[[1,ct]],
                                      title = titles["RNA"],
                                      color = colors[ct] )
  
  methy <- scatterplot_truevsestimate(merged_data, x = ct,
                                      y = celltype_trios[[2,ct]],
                                      title = titles["methy"],
                                      color = colors[ct])
  
  avg <- scatterplot_truevsestimate(merged_data, x = ct,
                                    y = celltype_trios[[3,ct]],
                                    title = titles["avg"],
                                    color = colors[ct])
  
  resplots[[ct]] <- ggarrange(RNA, methy, avg, ncol = 3, nrow = 1, align = "hv")
  }
  
  df_sup4 <- ggarrange(plotlist = resplots,  labels = names(celltype_trios), hjust = 0,  ncol = 1, nrow = 3, font.label = list(size = 20, color = "black"), align = "hv")
  
  df_sup4 <- annotate_figure(df_sup4,
                             top = text_grob(name, color = "black", size = 30),
                             left = text_grob("Estimated fractions", color = "black", size = 20, rot = 90),
                             bottom = text_grob("H&E estimates", color = "black", size = 20))
  pdf_name <- paste("ALL_", name, ".pdf", sep = "")
  ggsave(pdf_name, dpi = "print", width = 210, height = 297, units = "mm", scale = 2)
  }
```

# General Data loading

```{r}
read_csv("/mnt/SERVER-CRCT-STORAGE/CRCT21/data/deconvolution_for_gemdecan/all_deconvolutions_all_TCGA.txt") %>%
  mutate_at("Samples", str_remove_all, ".01A*") %>%
  mutate_at("Samples", str_replace_all, "-", ".") %>% 
  group_by(Samples) %>%
  summarise_all(mean) -> tcga_deconv

read_tsv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/facs/Aran_facs.csv") %>%
  mutate_at("Sample_ID", str_remove_all, ".01A*") %>%
  mutate_at("Sample_ID", str_replace_all, "-", ".") -> Aran_all_facs


read_csv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/HE_fractions.csv") %>%
  dplyr::select(-c(...1)) %>%
  mutate_at("ParticipantBarcode", str_remove_all, ".01A*") %>%
  mutate_at("ParticipantBarcode", str_replace_all, "-", ".") -> HE_all_TCGA

```

# COAD 

```{r}
read.table("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/meth/COAD.txt", sep = "\t", header = T) %>% as_tibble(rownames = "rowname") -> COAD_methy_decon_ # problem with 1st column missing colname
Aran_all_facs %>% dplyr::filter(Cancer_type == "COAD", CPE != "NaN") -> Facs_COAD 
HE_all_TCGA %>% dplyr::filter(Study == "COAD") -> HE_COAD

Comm_samples <- Reduce(intersect, list(HE_COAD$ParticipantBarcode,
                                       Facs_COAD$Sample_ID,
                                       tcga_deconv$Samples,
                                       COAD_methy_decon_$rowname))

Facs_COAD %>% dplyr::filter(Sample_ID %in% Comm_samples) %>%
  arrange(factor(Sample_ID, levels = Comm_samples)) -> Facs_COAD_modif

HE_COAD %>% dplyr::filter(ParticipantBarcode %in% Comm_samples) %>%
  arrange(factor(ParticipantBarcode, levels = Comm_samples)) -> HE_COAD_modif

COAD_methy_decon_ %>% dplyr::filter(rowname %in% Comm_samples) %>%
  arrange(factor(rowname, levels = Comm_samples)) -> COAD_methy_decon

tcga_deconv %>% filter(Samples %in% Comm_samples) %>%
  arrange(factor(Samples, levels = Comm_samples)) -> COAD_RNA_decon


stopifnot(HE_COAD_modif$ParticipantBarcode == Facs_COAD_modif$Sample_ID)
bind_cols(Facs_COAD_modif, HE_COAD_modif) %>% dplyr::select(-c(ParticipantBarcode, Study)) -> true_COAD


COAD_scatterplots <- scatterplot_wrapper(true_df = true_COAD,
                                         RNA_estimates = COAD_RNA_decon,
                                         methy_estimates = COAD_methy_decon,
                                         RNA_meth = "Epidish_BPRNACan_",
                                         name = "COAD")
```
RNA, methylation, and averaged values of correlation across a : lymphocytes, b: macrophages , c : neutrophils, using the BPRNACan and BPMetCan signatures on EpiDish.

# LUAD

```{r}
read.table("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/meth/LUAD.txt", sep = "\t", header = T) %>% as_tibble(rownames = "rowname") -> LUAD_methy_decon_ # problem with 1st column missing colname
Aran_all_facs %>% dplyr::filter(Cancer_type == "LUAD", CPE != "NaN") -> Facs_LUAD 
HE_all_TCGA %>% dplyr::filter(Study == "LUAD") -> HE_LUAD

Comm_samples <- Reduce(intersect, list(HE_LUAD$ParticipantBarcode,
                                       Facs_LUAD$Sample_ID,
                                       tcga_deconv$Samples,
                                       LUAD_methy_decon_$rowname))

Facs_LUAD %>% dplyr::filter(Sample_ID %in% Comm_samples) %>%
  arrange(factor(Sample_ID, levels = Comm_samples)) -> Facs_LUAD_modif

HE_LUAD %>% dplyr::filter(ParticipantBarcode %in% Comm_samples) %>%
  arrange(factor(ParticipantBarcode, levels = Comm_samples)) -> HE_LUAD_modif

LUAD_methy_decon_ %>% dplyr::filter(rowname %in% Comm_samples) %>%
  arrange(factor(rowname, levels = Comm_samples)) -> LUAD_methy_decon

tcga_deconv %>% filter(Samples %in% Comm_samples) %>%
  arrange(factor(Samples, levels = Comm_samples)) -> LUAD_RNA_decon


stopifnot(HE_LUAD_modif$ParticipantBarcode == Facs_LUAD_modif$Sample_ID)
bind_cols(Facs_LUAD_modif, HE_LUAD_modif) %>% dplyr::select(-c(ParticipantBarcode, Study)) -> true_LUAD


LUAD_scatterplots <- scatterplot_wrapper(true_df = true_LUAD,
                                         RNA_estimates = LUAD_RNA_decon,
                                         methy_estimates = LUAD_methy_decon,
                                         RNA_meth = "Epidish_BPRNACan_",
                                         name = "LUAD")
```
RNA, methylation, and averaged values of correlation across a : lymphocytes, b:  macrophages, c :  neutrophils, using the BPRNACan and BPMetCan signatures on EpiDish.

# LUSC

```{r}
read.table("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/meth/LUSC.txt", sep = "\t", header = T) %>% as_tibble(rownames = "rowname") -> LUSC_methy_decon_ # problem with 1st column missing colname
Aran_all_facs %>% dplyr::filter(Cancer_type == "LUSC", CPE != "NaN") -> Facs_LUSC 
HE_all_TCGA %>% dplyr::filter(Study == "LUSC") -> HE_LUSC

Comm_samples <- Reduce(intersect, list(HE_LUSC$ParticipantBarcode,
                                       Facs_LUSC$Sample_ID,
                                       tcga_deconv$Samples,
                                       LUSC_methy_decon_$rowname))

Facs_LUSC %>% dplyr::filter(Sample_ID %in% Comm_samples) %>%
  arrange(factor(Sample_ID, levels = Comm_samples)) -> Facs_LUSC_modif

HE_LUSC %>% dplyr::filter(ParticipantBarcode %in% Comm_samples) %>%
  arrange(factor(ParticipantBarcode, levels = Comm_samples)) -> HE_LUSC_modif

LUSC_methy_decon_ %>% dplyr::filter(rowname %in% Comm_samples) %>%
  arrange(factor(rowname, levels = Comm_samples)) -> LUSC_methy_decon

tcga_deconv %>% filter(Samples %in% Comm_samples) %>%
  arrange(factor(Samples, levels = Comm_samples)) -> LUSC_RNA_decon


stopifnot(HE_LUSC_modif$ParticipantBarcode == Facs_LUSC_modif$Sample_ID)
bind_cols(Facs_LUSC_modif, HE_LUSC_modif) %>% dplyr::select(-c(ParticipantBarcode, Study)) -> true_LUSC


LUSC_scatterplots <- scatterplot_wrapper(true_df = true_LUSC,
                                         RNA_estimates = LUSC_RNA_decon,
                                         methy_estimates = LUSC_methy_decon,
                                         RNA_meth = "Epidish_BPRNACan_",
                                         name = "LUSC")

```
RNA, methylation, and averaged values of correlation across a : lymphocytes, b:  macrophages, c :  neutrophils, using the BPRNACan and BPMetCan signatures on EpiDish.

# PRAD 

```{r}

read.table("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/meth/PRAD.txt", sep = "\t", header = T) %>% as_tibble(rownames = "rowname") -> PRAD_methy_decon_ # problem with 1st column missing colname
Aran_all_facs %>% dplyr::filter(Cancer_type == "PRAD", CPE != "NaN") -> Facs_PRAD 
HE_all_TCGA %>% dplyr::filter(Study == "PRAD") -> HE_PRAD

Comm_samples <- Reduce(intersect, list(HE_PRAD$ParticipantBarcode,
                                       Facs_PRAD$Sample_ID,
                                       tcga_deconv$Samples,
                                       PRAD_methy_decon_$rowname))

Facs_PRAD %>% dplyr::filter(Sample_ID %in% Comm_samples) %>%
  arrange(factor(Sample_ID, levels = Comm_samples)) -> Facs_PRAD_modif

HE_PRAD %>% dplyr::filter(ParticipantBarcode %in% Comm_samples) %>%
  arrange(factor(ParticipantBarcode, levels = Comm_samples)) -> HE_PRAD_modif

PRAD_methy_decon_ %>% dplyr::filter(rowname %in% Comm_samples) %>%
  arrange(factor(rowname, levels = Comm_samples)) -> PRAD_methy_decon

tcga_deconv %>% filter(Samples %in% Comm_samples) %>%
  arrange(factor(Samples, levels = Comm_samples)) -> PRAD_RNA_decon


stopifnot(HE_PRAD_modif$ParticipantBarcode == Facs_PRAD_modif$Sample_ID)
bind_cols(Facs_PRAD_modif, HE_PRAD_modif) %>% dplyr::select(-c(ParticipantBarcode, Study)) -> true_PRAD


PRAD_scatterplots <- scatterplot_wrapper(true_df = true_PRAD,
                                         RNA_estimates = PRAD_RNA_decon,
                                         methy_estimates = PRAD_methy_decon,
                                         RNA_meth = "Epidish_BPRNACan_",
                                         name = "PRAD")
```
RNA, methylation, and averaged values of correlation across a : lymphocytes, b:  macrophages, c :  neutrophils, using the BPRNACan and BPMetCan signatures on EpiDish.

# BRCA

```{r}
read.table("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/meth/BRCA.txt", sep = "\t", header = T) %>% as_tibble(rownames = "rowname") -> BRCA_methy_decon_ # problem with 1st column missing colname
Aran_all_facs %>% dplyr::filter(Cancer_type == "BRCA", CPE != "NaN") -> Facs_BRCA 
HE_all_TCGA %>% dplyr::filter(Study == "BRCA") -> HE_BRCA

Comm_samples <- Reduce(intersect, list(HE_BRCA$ParticipantBarcode,
                                       Facs_BRCA$Sample_ID,
                                       tcga_deconv$Samples,
                                       BRCA_methy_decon_$rowname))

Facs_BRCA %>% dplyr::filter(Sample_ID %in% Comm_samples) %>%
  arrange(factor(Sample_ID, levels = Comm_samples)) -> Facs_BRCA_modif

HE_BRCA %>% dplyr::filter(ParticipantBarcode %in% Comm_samples) %>%
  arrange(factor(ParticipantBarcode, levels = Comm_samples)) -> HE_BRCA_modif

BRCA_methy_decon_ %>% dplyr::filter(rowname %in% Comm_samples) %>%
  arrange(factor(rowname, levels = Comm_samples)) -> BRCA_methy_decon

tcga_deconv %>% filter(Samples %in% Comm_samples) %>%
  arrange(factor(Samples, levels = Comm_samples)) -> BRCA_RNA_decon


stopifnot(HE_BRCA_modif$ParticipantBarcode == Facs_BRCA_modif$Sample_ID)
bind_cols(Facs_BRCA_modif, HE_BRCA_modif) %>% dplyr::select(-c(ParticipantBarcode, Study)) -> true_BRCA


BRCA_scatterplots <- scatterplot_wrapper(true_df = true_BRCA,
                                         RNA_estimates = BRCA_RNA_decon,
                                         methy_estimates = BRCA_methy_decon,
                                         RNA_meth = "Epidish_BPRNACan_",
                                         name = "BRCA")
```
RNA, methylation, and averaged values of correlation across a : lymphocytes, b:  macrophages, c :  neutrophils, using the BPRNACan and BPMetCan signatures on EpiDish.

# BLCA

```{r}
read.table("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/meth/BLCA.txt", sep = "\t", header = T) %>% as_tibble(rownames = "rowname") -> BLCA_methy_decon_ # problem with 1st column missing colname
Aran_all_facs %>% dplyr::filter(Cancer_type == "BLCA", CPE != "NaN") -> Facs_BLCA 
HE_all_TCGA %>% dplyr::filter(Study == "BLCA") -> HE_BLCA

Comm_samples <- Reduce(intersect, list(HE_BLCA$ParticipantBarcode,
                                       Facs_BLCA$Sample_ID,
                                       tcga_deconv$Samples,
                                       BLCA_methy_decon_$rowname))

Facs_BLCA %>% dplyr::filter(Sample_ID %in% Comm_samples) %>%
  arrange(factor(Sample_ID, levels = Comm_samples)) -> Facs_BLCA_modif

HE_BLCA %>% dplyr::filter(ParticipantBarcode %in% Comm_samples) %>%
  arrange(factor(ParticipantBarcode, levels = Comm_samples)) -> HE_BLCA_modif

BLCA_methy_decon_ %>% dplyr::filter(rowname %in% Comm_samples) %>%
  arrange(factor(rowname, levels = Comm_samples)) -> BLCA_methy_decon

tcga_deconv %>% filter(Samples %in% Comm_samples) %>%
  arrange(factor(Samples, levels = Comm_samples)) -> BLCA_RNA_decon


stopifnot(HE_BLCA_modif$ParticipantBarcode == Facs_BLCA_modif$Sample_ID)
bind_cols(Facs_BLCA_modif, HE_BLCA_modif) %>% dplyr::select(-c(ParticipantBarcode, Study)) -> true_BLCA


BLCA_scatterplots <- scatterplot_wrapper(true_df = true_BLCA,
                                         RNA_estimates = BLCA_RNA_decon,
                                         methy_estimates = BLCA_methy_decon,
                                         RNA_meth = "Epidish_BPRNACan_",
                                         name = "BLCA")
```
RNA, methylation, and averaged values of correlation across a : lymphocytes, b:  macrophages, c :  neutrophils, using the BPRNACan and BPMetCan signatures on EpiDish.


## UCEC 

```{r}
read.table("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/meth/UCEC.txt", sep = "\t", header = T) %>% as_tibble(rownames = "rowname") -> UCEC_methy_decon_ # problem with 1st column missing colname
Aran_all_facs %>% dplyr::filter(Cancer_type == "UCEC", CPE != "NaN") -> Facs_UCEC 
HE_all_TCGA %>% dplyr::filter(Study == "UCEC") -> HE_UCEC

Comm_samples <- Reduce(intersect, list(HE_UCEC$ParticipantBarcode,
                                       Facs_UCEC$Sample_ID,
                                       tcga_deconv$Samples,
                                       UCEC_methy_decon_$rowname))

Facs_UCEC %>% dplyr::filter(Sample_ID %in% Comm_samples) %>%
  arrange(factor(Sample_ID, levels = Comm_samples)) -> Facs_UCEC_modif

HE_UCEC %>% dplyr::filter(ParticipantBarcode %in% Comm_samples) %>%
  arrange(factor(ParticipantBarcode, levels = Comm_samples)) -> HE_UCEC_modif

UCEC_methy_decon_ %>% dplyr::filter(rowname %in% Comm_samples) %>%
  arrange(factor(rowname, levels = Comm_samples)) -> UCEC_methy_decon

tcga_deconv %>% filter(Samples %in% Comm_samples) %>%
  arrange(factor(Samples, levels = Comm_samples)) -> UCEC_RNA_decon


stopifnot(HE_UCEC_modif$ParticipantBarcode == Facs_UCEC_modif$Sample_ID)
bind_cols(Facs_UCEC_modif, HE_UCEC_modif) %>% dplyr::select(-c(ParticipantBarcode, Study)) -> true_UCEC


UCEC_scatterplots <- scatterplot_wrapper(true_df = true_UCEC,
                                         RNA_estimates = UCEC_RNA_decon,
                                         methy_estimates = UCEC_methy_decon,
                                         RNA_meth = "Epidish_BPRNACan_",
                                         name = "UCEC")
```
RNA, methylation, and averaged values of correlation across a : lymphocytes, b:  macrophages, c :  neutrophils, using the BPRNACan3D and BPMetCan signatures on EpiDish.

## CESC

```{r}
read.table("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/meth/CESC.txt", sep = "\t", header = T) %>% as_tibble(rownames = "rowname") -> CESC_methy_decon_ # problem with 1st column missing colname
Aran_all_facs %>% dplyr::filter(Cancer_type == "CESC", CPE != "NaN") -> Facs_CESC 
HE_all_TCGA %>% dplyr::filter(Study == "CESC") -> HE_CESC

Comm_samples <- Reduce(intersect, list(HE_CESC$ParticipantBarcode,
                                       Facs_CESC$Sample_ID,
                                       tcga_deconv$Samples,
                                       CESC_methy_decon_$rowname))

Facs_CESC %>% dplyr::filter(Sample_ID %in% Comm_samples) %>%
  arrange(factor(Sample_ID, levels = Comm_samples)) -> Facs_CESC_modif

HE_CESC %>% dplyr::filter(ParticipantBarcode %in% Comm_samples) %>%
  arrange(factor(ParticipantBarcode, levels = Comm_samples)) -> HE_CESC_modif

CESC_methy_decon_ %>% dplyr::filter(rowname %in% Comm_samples) %>%
  arrange(factor(rowname, levels = Comm_samples)) -> CESC_methy_decon

tcga_deconv %>% filter(Samples %in% Comm_samples) %>%
  arrange(factor(Samples, levels = Comm_samples)) -> CESC_RNA_decon


stopifnot(HE_CESC_modif$ParticipantBarcode == Facs_CESC_modif$Sample_ID)
bind_cols(Facs_CESC_modif, HE_CESC_modif) %>% dplyr::select(-c(ParticipantBarcode, Study)) -> true_CESC


CESC_scatterplots <- scatterplot_wrapper(true_df = true_CESC,
                                         RNA_estimates = CESC_RNA_decon,
                                         methy_estimates = CESC_methy_decon,
                                         RNA_meth = "Epidish_BPRNACan_",
                                         name = "CESC")
```
RNA, methylation, and averaged values of correlation across a : lymphocytes, b:  macrophages, c :  neutrophils, using the BPRNACan and BPMetCan signatures on EpiDish.


## SKCM

```{r}
read.table("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/meth/SKCM.txt", sep = "\t", header = T) %>% as_tibble(rownames = "rowname") -> SKCM_methy_decon_ # problem with 1st column missing colname
Aran_all_facs %>% dplyr::filter(Cancer_type == "SKCM", CPE != "NaN") -> Facs_SKCM 
HE_all_TCGA %>% dplyr::filter(Study == "SKCM") -> HE_SKCM

Comm_samples <- Reduce(intersect, list(HE_SKCM$ParticipantBarcode,
                                       Facs_SKCM$Sample_ID,
                                       tcga_deconv$Samples,
                                       SKCM_methy_decon_$rowname))

Facs_SKCM %>% dplyr::filter(Sample_ID %in% Comm_samples) %>%
  arrange(factor(Sample_ID, levels = Comm_samples)) -> Facs_SKCM_modif

HE_SKCM %>% dplyr::filter(ParticipantBarcode %in% Comm_samples) %>%
  arrange(factor(ParticipantBarcode, levels = Comm_samples)) -> HE_SKCM_modif

SKCM_methy_decon_ %>% dplyr::filter(rowname %in% Comm_samples) %>%
  arrange(factor(rowname, levels = Comm_samples)) -> SKCM_methy_decon

tcga_deconv %>% filter(Samples %in% Comm_samples) %>%
  arrange(factor(Samples, levels = Comm_samples)) -> SKCM_RNA_decon


stopifnot(HE_SKCM_modif$ParticipantBarcode == Facs_SKCM_modif$Sample_ID)
bind_cols(Facs_SKCM_modif, HE_SKCM_modif) %>% dplyr::select(-c(ParticipantBarcode, Study)) -> true_SKCM


SKCM_scatterplots <- scatterplot_wrapper(true_df = true_SKCM,
                                         RNA_estimates = SKCM_RNA_decon,
                                         methy_estimates = SKCM_methy_decon,
                                         RNA_meth = "Epidish_BPRNACan_",
                                         name = "SKCM")
```
RNA, methylation, and averaged values of correlation across a : lymphocytes, b:  macrophages, c :  neutrophils, using the BPRNACan and BPMetCan signatures on EpiDish.

# PDF merge
```{r}
system("pdfunite ALL_*.pdf sup_fig4.pdf")
```